The \dealii Library, Version 9.7

### 2025-08-07 9.7/paper.tex
Remove Magdalena's affiliation.
She isn't a coauthor this time.
Fix more minor typos

T.~Heister were also partiallty supported by NSF Awards OAC-2015848 and EAR-1925575.

@@

M.~Maier was partially supported by NSF Award DMS-2045636 and and by the
Air Force Office of Scientific Research under grant/contract number
FA9550-23-1-0007.

@@

M.~Schreter-Fleischhacker was supported by the Austrian Science Fund (FWF) Schrödinger Fellowship (project number: J4577) and by the European Research Council
through the ERC Starting Grant ExcelAM (project number: 101117579).

>>>>

T.~Heister were also partially supported by NSF Awards OAC-2015848 and EAR-1925575.

@@

M.~Maier was partially supported by NSF Award DMS-2045636 and by the
Air Force Office of Scientific Research under grant/contract number
FA9550-23-1-0007.

@@
